---
title: "Statistical Inference Project Two - ToothGrowth"
author: "Ivan Liu"
date: "Sunday, September 07, 2014"
output: html_document
---

This is a basic statistical inference data analysis. In this report, we're going to analyze the ToothGrowth data in the R datasets package. 

```{r, warning=FALSE, message=FALSE, fig.height=4,fig.width=8,fig.align='center'}
# Setup and run the simulation
setwd('C:\\Users\\Ivan.Liuyanfeng\\Desktop\\Data_Mining_Work_Space\\Data-Science-Statistical-Inference\\project')
library(ggplot2)
library(datasets)
```

---

### Section One
Load the ToothGrowth data and perform some basic exploratory data analyses

```{r, warning=FALSE, message=FALSE, fig.height=4,fig.width=8,fig.align='center'}
data(ToothGrowth)
head(ToothGrowth)
g1 <- ggplot(ToothGrowth, aes(x=factor(dose),y=len,fill=factor(dose)))
g1 + geom_boxplot(notch=T) + facet_grid(.~supp) + 
    scale_x_discrete("Dosage in mg") + 
    scale_y_continuous("Length of Teeth") + 
    ggtitle("Exploratory data analyses")
```

The above diagram reveals that longer teeth tend to use higher dosage.

---

### Section Two
Provide a basic summary of the data.

```{r, warning=FALSE, message=FALSE, fig.height=4,fig.width=8,fig.align='center'}

```

---

### Section Three
Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose. (Use the techniques from class even if there's other approaches worth considering)

```{r, warning=FALSE, message=FALSE, fig.height=4,fig.width=8,fig.align='center'}

```

---

### Section Four
State your conclusions and the assumptions needed for your conclusions. 

```{r, warning=FALSE, message=FALSE, fig.height=4,fig.width=8,fig.align='center'}

```

---

<b>Thank you for reading!</b></br>
<b>Ivan Liu</b></br>
<b>07/09/2014</b></br>